---
title: "STAT 545A Troubleshooting Exercise for Milestone 1"
output: github_document
---

There are **3 code chunks with errors** in this Rmd. Your objective is to fix all of the errors in this worksheet. Make sure to indicate what lines you changed and why (by commenting \# in the code).

For the purpose of grading, each erroneous code chunk is equally weighted.

## Welcome to R and Rmd!

This document is written in **R Markdown**. We'll use this document to explore the `mtcars` dataset.

First, let's store the current date as a variable. We can use the function `Sys.Date` with no arguments to get the current date:

```{r, error = TRUE}
## ERROR 1 ##
# Line 19 Max: Variable name can't start with special characters, change the character name to today
# We changed "today <- Sys.Date()" to "today_ <- Sys.Date()" (removal of the proceeding underscore in object name), to specify exactly which changes were made
# _today_ <- Sys.Date()
today <- Sys.Date()
```

You may notice that, although an error might appear in these cells, this Rmd file knits just fine. That's because the `error = TRUE` *chunk option* is included in each chunk, allowing the Rmd file to knit, even when an error is encountered.

Now, let's load the `tidyverse` (meta-) package:

```{r, error = TRUE}
## ERROR 2 ##
# Line 30 Max: Wrong function for accessing the package, should be library()
# We changed "libraries(tidyverse)" to the correct call: "library(tidyverse)".
# libraries(tidyverse)
library(tidyverse)
```

By loading the tidyverse, a function called `glimpse` has been made available. This function is useful for viewing a data set. Let's take a look at the `mtcars` dataset by applying the `glimpse` function to `mtcars`!

```{r, error = TRUE}
## ERROR 3 ##
# Line 39 Max: Wrong way to apply functions to dtl, should be glimpse()
# we changed "glimpse mtcars" to "glimpse(mtcars)" (The object to which the function is being applied (here: mtcars) should be bracketed beside the function.
# glimpse mtcars
glimpse(mtcars)
```

## Attribution

Thanks to Icíar Fernández Boyano for coming up with most of this worksheet.
